\textbf{Designing a Virtual Security Management Layer for Cloud Content}

### 2016-02-02 tex/paper.tex
Added some CDN security details

\fix Clarify problem definition and research questions

@@

\subsection{Approach}
\fix Write about how the approach is similar to BLP and that it is not a proof etc
As this work only presents an informal model of how the system is designed it can not be regarded as
a proof for the actual implementation of the system to be flawless. The model should how ever give a 
strong idea of the soundness of the designed system.

\subsection{Elements of the Model}
\fix Mathematical formal description of how the system works

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Set} & \textbf{Elements} & \textbf{Semantics} \\ \hline
        C   & $c_0\dots c_n$                & Containers; folders in the virtual file system\\ \hline
        F   & $f_0\dots f_n$                & Files; files, images, videos\\ \hline
        M   & $m_0\dots m_n$                & Content; Meta-data for files\\ \hline
        U   & $u_0\dots u_n$                & Users; registered users in the system\\ \hline
        A   & $A[u_0,c_0]\dots A[u_n, c_n]$ & Access matrix; describes what containers users have access to\\ \hline
    \end{tabular}
\end{center}

@@

\fix Add content, m
\begin{equation}
    \begin{split}
        u \in U \text{ can read } c \in C & \Iff u \in A[u,c] \\
        u \in U \text{ can write } c \in C & \Iff u \in A[u,c] \text{ and readonly } \notin c \\
        u \in U \text{ can delete } m \in c & \Iff u \in A[u,c] \text{ and readonly } \notin c \\
        u \nexists U \text{ can delete } f \in F \\
        \forall c \in C, \quad \exists u \in U & \mid a \in A[u,c] 
    \end{split}
\end{equation}

@@

\subsection{Consequences of modification}
\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Action} & \textbf{Semantics} \\ \hline
        u, read(o)            & User u reads object o\\ \hline
        u, write(o)           & User u writes object o\\ \hline
        u, copy(o)            & User u copies object o and the copy gets a new ID\\ \hline
        u, change(o)          & User u locally changes object o \\ \hline
        u, modify(o', o)      & User u globally modifies object o based on object o'\\ \hline
        u, delete(o)          & User u deletes object o\\ \hline
        u, snapshot(o)        & User u takes a snapshot of object o \\ \hline
    \end{tabular}
\end{center}

@@

\begin{equation} \label{eq:contentupdate}
    \begin{split}
        m' & = u, read(m) \land \\
        m'' & = u, change(m') \land \\
        m''' & = u, modify(m'', m) \Implies \\
        m''' & \in M \land m \not \in M
    \end{split}
\end{equation}
If a user reads content and then writes to it, the content is directly changed

\begin{equation} \label{eq:containerupdate}
    \begin{split}
        c' & = u, read(c) \land \\
        c'' & = u, change(c') \land \\
        c''' & = u, modify(c'', c) \Implies \\
        c''' & \in C \land c \not \in C
    \end{split}
\end{equation}
If a user reads a container and then writes to it, the container is directly changed

@@

As a result of consequence~\ref{eq:contentupdate} and ~\ref{eq:containerupdate} there can be race
conditions where the last write wins. This could be solved by locks or transactions, but as updates
are not based on each other, the trade-off for this inconsistency to scalability and speed is
intentional. However as can also be seen in consequence~\ref{eq:fileupdate}, if a file is
removed from a content that file is not removed from the set of files, even though its modification
process is not the last one to write to the content. This is necessary as a file can be referenced
from several content and the removal process can not atomically ensure that the file is not referred
to by another content. This results in a lot of files in the system which are not referenced from
anywhere. This can be solved by either making each file keep track of how many times it is referred
to and also make it possible to check this number and delete the file in an atomic fashion. An
easier approach would be to have a garbage collector which locks parts of the system momentarily
meanwhile it removes files which are not referenced.

@@

\newpage
\section{Implementation}
\subsection{Background}
\subsubsection{About Uprise}
Uprise is a company based in Uppsala, Sweden. It is an EA studio focussing on creating great gaming
experiences, which means that they are mostly not focussed on the actual gameplay which other EA 
studios like DICE is.

\subsubsection{The current system}
Today a system called battlebinary~\cite{BATTLEBINARY} is used for managing and uploading files,
mostly images, to content delivery networks. The current system does not make use out of the
security features that the CDN's are offering, instead it uses a form of security by obscurity. When
a file is uploaded to a CDN it is open for the public, but its filename is composed out of its
original filename concatenated with a part of the MD5 hash of the content of the file, which makes
it an extremely hard process to access the file on the CDN without access to the original file or a
reference to the URI.

@@

\par
As the project tree is built by querying documents parent id one optimisation that could be done was
to create an index of the documents parent ids. This drastically improved the size of the tree that
the server was able to handle within the time out, going from being able to handle 4000 documents to
at least 50000 documents, which the browser instead will have problems displaying, represented in the 
UI, without lag.

@@

\subsubsection{Security of the system}
\paragraph{Authorization}
The authorization of users in the system is currently being handled by LDAP~\cite{LDAP}, as Perius is mainly
focussed at being deployed in internal networks which usually has an LDAP service enabled. LDAP also
makes it easier for the user to login as no separate account is needed for Perius and thus the user
can use the same account as for all the LDAP connected services on the internal network.

\paragraph{Audit logs}

>>>>

\fix Clarify problem definition and research questions
\section{Background}
\subsection{About Uprise}
Uprise is a company based in Uppsala, Sweden. It is an EA studio focussing on creating great gaming
experiences, which means that they are mostly not focussed on the actual gameplay which other EA 
studios like DICE is.

@@

\subsection{Approach}
\fix Write about how the approach is similar to BLP and that it is not a proof etc

As this work only presents an informal model of how the system is designed it can not be regarded as
a proof for the actual implementation of the system to be flawless. The model should how ever give a 
strong idea of the soundness of the designed system.

\subsection{Elements of the Model}
\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Set} & \textbf{Elements} & \textbf{Semantics} \\ \hline
        C   & $c_0\dots c_n$                & Containers; folders in the virtual file system\\ \hline
        F   & $f_0\dots f_n$                & Files; files, images, videos\\ \hline
        M   & $m_0\dots m_n$                & Content; Meta-data for files\\ \hline
        U   & $u_0\dots u_n$                & Users; registered users in the system\\ \hline
        A   & $A[u_0,c_0]\dots A[u_n, c_n]$ & Access matrix; describes what containers users have access to\\ \hline
    \end{tabular}
\end{center}

@@

\begin{equation}
    \begin{split}
        u \in U \text{ can read } c \in C & \Iff u \in A[u,c] \\
        u \in U \text{ can write } c \in C & \Iff u \in A[u,c] \text{ and readonly } \notin c \\
        u \in U \text{ can delete } m \in c & \Iff u \in A[u,c] \text{ and readonly } \notin c \\
        u \nexists U \text{ can delete } f \in F \\
        \forall c \in C, \quad \exists u \in U & \mid a \in A[u,c] 
    \end{split}
\end{equation}

@@

\label{sec:conseq}
\subsection{Consequences of modification}

\begin{center}
    \begin{tabular}{ | l | l | l | p{5cm} |}
        \hline
        \textbf{Action} & \textbf{Semantics} \\ \hline
        u, read(o)            & User u reads object o\\ \hline
        u, write(o)           & User u writes object o\\ \hline
        u, copy(o)            & User u copies object o and the copy gets a new ID\\ \hline
        u, change(o)          & User u locally changes object o \\ \hline
        u, modify(o', o)      & User u globally modifies object o based on object o'\\ \hline
        u, delete(o)          & User u deletes object o\\ \hline
        u, snapshot(o)        & User u takes a snapshot of object o \\ \hline
    \end{tabular}
\end{center}

@@

\begin{equation} \label{eq:contentupdate}
    \begin{split}
        m' & = u, read(m) \land \\
        m'' & = u, change(m') \land \\
        m''' & = u, modify(m'', m) \Implies \\
        m''' & \in M \land m \not \in M
    \end{split}
\end{equation}
If a user reads content and then writes to it, the content is directly changed.

\begin{equation} \label{eq:containerupdate}
    \begin{split}
        c' & = u, read(c) \land \\
        c'' & = u, change(c') \land \\
        c''' & = u, modify(c'', c) \Implies \\
        c''' & \in C \land c \not \in C
    \end{split}
\end{equation}
If a user reads a container and then writes to it, the container is directly changed.

@@

As a result of consequence~\ref{eq:contentupdate} and~\ref{eq:containerupdate} there can be race
conditions where the last write wins. This could be solved by locks or transactions, but as updates
are not based on each other, the trade-off for this inconsistency to scalability and speed is
intentional. However as can also be seen in consequence~\ref{eq:fileupdate}, if a file is
removed from a content that file is not removed from the set of files, even though its modification
process is not the last one to write to the content. This is necessary as a file can be referenced
from several content and the removal process can not atomically ensure that the file is not referred
to by another content. This results in a lot of files in the system which are not referenced from
anywhere. This can be solved by either making each file keep track of how many times it is referred
to and also make it possible to check this number and delete the file in an atomic fashion. An
easier approach would be to have a garbage collector which locks parts of the system momentarily
meanwhile it removes files which are not referenced.

There is also the chance to have content and containers that are not referenced from anywhere and
result in being garbage in the system. This could happen as a result of consequence~\ref{eq:delete}
in combination with any of the other consequences listed in Section~\ref{sec:conseq}. The basic idea
is that an entity is deleted meanwhile another is created or modified to have that entity as its
parent and thus creating a separate tree that can not be reached from the root node of the project.

@@

\newpage
\section{Implementation}
\subsection{Background}
\subsubsection{The current system}
Today a system called battlebinary~\cite{BATTLEBINARY} is used for managing and uploading files,
mostly images, to content delivery networks. The current system does not make use out of the
security features that the CDN's are offering, instead it uses a form of security by obscurity. When
a file is uploaded to a CDN it is open for the public, but its filename is composed out of its
original filename concatenated with a part of the MD5 hash of the content of the file, which makes
it an extremely hard process to access the file on the CDN without access to the original file or a
reference to the URI.

@@

\par
As the project tree is built by querying documents parent id an optimisation that could be done was
to create an index of the documents parent ids. This drastically improved the size of the tree that
the server was able to handle within the time out, going from being able to handle 4000 documents in 
one tree to at least 50000 documents, which the browser instead will have problems displaying, 
represented in the UI, without lag.

@@

\subsubsection{Security of the system}
\subsubsubsection{Authorization}
The authorization of users in the system is currently being handled by LDAP~\cite{LDAP}, as Perius 
is mainly focussed at being deployed in internal networks which usually has an LDAP service enabled. 
LDAP also makes it easier for the user to login as no separate account is needed for Perius and 
thus the user can use the same account as for all the LDAP connected services on the internal 
network.

\subsubsubsection{Audit logs}

\subsubsubsection{CDN Connections}
\fix Describe how the CDN connections are encrypted and secure.

When uploading files to the CDN networks their TLS/SSL protected API's are used to ensure that no
data leaks through packet sniffing etc. The files are grouped corresponding to their parent
containers in Perius, which makes it possible to handle the security settings for all files in a
group at once, without having to traverse through the tree in Perius.

\fix Describe the different CDN mechanisms, like signed cookies and urls
